<span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>

### 2014-09-03 ants2015build.Rmd
WIP: regular update

## ANTs: Saving society \$\$\$

starting with neuroscience ...

@@

>>>>

## Reproducibility

* Consider the recent paper: [Freesurfer, laplacian, DiReCT thickness in longitudinal stroke](http://ac.els-cdn.com/S2213158214001260/1-s2.0-S2213158214001260-main.pdf?_tid=8e6f5248-335d-11e4-ba4f-00000aab0f02&acdnat=1409743944_6615d59eb5709e6bcb1aca76450f7d93)

* We "pre-wrote" a comment: [Instrumentation bias in the use and evaluation of scientific software](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3766821/?report=reader)

* With these guys:

* <img src="figures/luis.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right: 3px;"><img src="figures/torsten.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right:3px;">

## Hired by Google

<img src="figures/luis.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right: 3px;"><img src="figures/torsten.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right:3px;"><img src="figures/gang.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right:3px;">

@@

## RKRNS

[link](stnava.github.io/RKRNS)

What mathematical encoding of language reflects both brain activity and 
"our" understanding of semantics?

## RIPMARC: Imputation, strutural networks, etc.

![](figures/ripmmarc_inter.png)

MICCAI 2014, Neuroimage 2015

## Big image registration
